---
title: "ML-project"
author: "wind"
date: "2015年12月26日"
output: html_document
---
This is homework of ML project.

## Clean the original files, since there are lots of NAs in the original dataset, using the excel to omnit the columns which contain the NAs.


```{r, cache= TRUE}
## Loading the needed libraries
library(caret)
library(randomForest)
library(dplyr)
# load the dataset with the selected feilds.
pmlTraining <- read.csv("C:/Users/windbike/Desktop/pml-training-clean.csv", header=TRUE)
## only 53 variations left
names(pmlTraining)
# load the test file
pmlTesting <- read.csv("C:/Users/windbike/Desktop/pml-testing.csv", header=TRUE)

```

## Create the partitions
```{r, cache = TRUE}

set.seed(1235)
inTrain <- createDataPartition(y=pmlTraining$classe,p=0.75, list=FALSE)
training <- pmlTraining[inTrain,]
testing <- pmlTraining[-inTrain,]

```
## Using the randomForest to train the model
```{r, cache= TRUE}

set.seed(1236)

modelFit1 <- randomForest(classe~., data=training, importance=TRUE, mtry = 7, na.action = na.omit)

# print the modelFit
modelFit1
```
## Using train(caret) with mothod RF to train the model

```{r, cache =TRUE}
set.seed(1236)

library(doParallel)
cl <- makeCluster(detectCores())
registerDoParallel(cl)
tc <- trainControl(method="boot",number=25)

modelFit2 <- train(classe~., data = training, method = "rf", trcControl=tc)

stopCluster(cl)
modelFit2

```


## Verify the testing dataset using the modelFit1 and modelFit2
```{r, cache= TRUE}
predictTest1 <- predict(modelFit1, newdata = testing)
predictTest1 <- data.frame(predictTest1)

predictTest2 <- predict(modelFit2, newdata = testing)
predictTest2 <- data.frame(predictTest2)

verify <- cbind(testing$classe, predictTest1, predictTest2)
verify <- mutate(verify, accurate1 = (testing$classe == predictTest1),accurate2 = (testing$classe == predictTest2)  )
# Calcuate the accurate of predication
rate1 <- sum(verify$accurate1 == TRUE)/length(verify$predictTest1)
rate2 <- sum(verify$accurate2 == TRUE)/length(verify$predictTest2)
# print rate by RandomForest
print(rate1)
# print rate by train with the method "rf"
print(rate2)

## the accurate is quite high, so use the 2 models to predict the 20 cases.
# predict the values of the submission

predict20 <- predict(modelFit1, newdata = pmlTesting)
print(predict20)

predict20 <- predict(modelFit2, newdata = pmlTesting)
print(predict20)

```
## The result is the same by two means of modeling.

